Predicting Donald Trump's win using Post-Stratification by Age Groups and Education Level

### 2020-11-02 outputs/paper/paper.Rmd
added graphs

---
title: "Predicting Donald Trump's win using Post-Stratification by Age Groups and Education Level"
author: "Kar Hian Ong and Fadlan Arif"
thanks:  "Code and data are available at: https://github.com/karhian/2020-election"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: "references.bib"
abstract: |
  | With the 2020 presedential election coming to an end soon, this paper looks into predicting who will win the the presidency this November.First sentence. By gathering data from the 2018 US census and survey data from nation scape, we were able to stratify our findings by age groups. After stratifying, we were able to more accurately model the population of the United States, letting us predict who will win. We find in this paper that (insert winner's name) is most likely to win the 2020 US election.
Keywords: "forecasting, US2020 election, Trump, Biden, multilevel regression with post-stratification" 
output:
  bookdown::pdf_document2:
toc: FALSE

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

@@

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

---
title: "Predicting Donald Trump's win using Post-Stratification by Age Groups and Education Level"
author: "Kar Hian Ong and Fadlan Arif"
thanks:  "Code and data are available at: https://github.com/karhian/2020-election"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: "references.bib"
abstract: |
  | With the 2020 presedential election coming to an end soon, this paper looks into predicting who will win the the presidency this November.First sentence. By gathering data from the 2018 US census and survey data from nation scape, we were able to stratify our findings by age groups. After stratifying, we were able to more accurately model the population of the United States, letting us predict who will win. We find in this paper that (insert winner's name) is most likely to win the 2020 US election.
Keywords: "forecasting, US2020 election, Trump, Biden, multilevel regression with post-stratification" 
output:
  bookdown::pdf_document2:
    fig_caption: yes        
    includes:  
      in_header: my_header.tex
toc: FALSE

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

@@

Figure \@ref(fig:age1) shows something

```{r age1, fig.cap = "Frequency of Age Groups for Population Data", echo = FALSE, fig.width=8, fig.height=4}
dataforgraph1 <- read.csv("../cleaned data/poststratification_cleaned.csv")
graph1 <- dataforgraph1 %>% 
  ggplot()+ geom_bar(aes(x=age_groups, fill = age_groups)) + 
  labs(x = "Age Groups", 
       y = "Number of People") 
graph1
```

Figure \@ref(fig:age2)  aslo shows something

```{r age2, fig.cap = "Frequency of Age Groups for Survery Data", echo = FALSE, fig.width=8, fig.height=4}
dataforgraph2 <- read.csv("../cleaned data/survey_cleaned.csv")
graph2 <- dataforgraph2 %>% 
  ggplot()+ geom_bar(aes(x=age_groups, fill = age_groups)) + 
  labs(x = "Age Groups", 
       y = "Number of People") 
graph2
```
```{r table1, fig.cap = "voting intention 2020", echo = FALSE, fig.width=8, fig.height=4}
#install.packages("scales")

table1 <- table(dataforgraph2$vote_2020)
table1
```
